\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Add Leo's abstract

>>>>

		In the field of computer-assisted composition, musical orchestration is probably the most empirical one and it has been traditionally taught in an intuitive and non formalized way. Computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers to explore new timbral possibilities by associating instrumental samples, which, combined, will sound perceptually similar to a target sound. In this paper, we will study the possibility of adding a source separation step to the target-assisted orchestration process. We first discuss the interest of this addition to improve the quality of orchestrations of multi-layered sounds. Second, we select several state of the art models from music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and we compare their efficiency for the task of orchestration. Our experiments show that the quality of orchestrations improved, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we discuss the interest of unsupervised methods compared to supervised methods in the case of assisted orchestration, where data are relatively scarce.
